### 2019-06-09 2-Chapters/2-Chapter/IEEE_WCNC_2018.git/IEEE_WCNC__2018__Paper__Lilian_Besson__07-17.tex
OMG c'est 00h23 un dimanche soir et je bosse !

\begin{small}
	\begin{figure}[h!]
		\centering
		\begin{framed}
		% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
		% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
		\begin{algorithm}[H]
			% XXX Input, data and output
			\KwIn{$N$ bandit algorithms, $\Alg_1, \dots, \Alg_N$, with $N \geq 2$}
			\KwIn{Number of arms, $K \geq 2$}
			\KwIn{Time horizon, $T \geq 1$, \textbf{not} used for the learning}
			\KwIn{A sequence of learning rates, $(\eta_t)_{t \geq 1}$}
			\KwData{Initial uniform distribution, $\pi^{0} = \cU([N])$}
			\KwResult{$\Alg_{\mathrm{aggr}}=\Aggr\left[\Alg_1, \dots, \Alg_N\right]$}
			% XXX Algorithm
			\For(\tcp*[f]{At every time step})
            {$t = 1, \dots, T$}{
				%
				% \tcp{First, run each algorithm $\Alg_a$}
				\For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
					$\Alg_a$ updates its internal state (e.g., \UCB{} indexes)\;
					It chooses $A_a(t) \in [K]$.
				}
				%
				% \tcp{The more algorithms have chosen arm $j$, the more probable it is to be chosen.}
				Let $p^{t}_j \eqdef \sum\limits_{a = 1}^{N} \pi^{t}_a \times \indic(\{A_a(t) = j\}), \;\forall 1\leq j \leq K$\;
				% \tcp*{Sum trusts}
				Then $\Alg_{\mathrm{aggr}}$ chooses arm $A(t) \sim p^{t}$\;
				% $\P(A(t)_{\mathrm{aggr}} = j) = p^{t}_j$
				% \tcp*{Sample once}
				%
				Give \emph{original} reward $(A(t), r(t))$ to \emph{each} $\Alg_a$ (maybe \emph{not} on its chosen arm)\;
				Compute an \emph{unbiased} estimate of the reward, $\widehat{r}(t) = r(t) / p^{t}_{A(t)}$\;
				% \tcp{Use bandit feedback to update $\pi^{t}$}
				% \tcp{Finally, use the instantaneous bandit feedback (reward $\ell_{A(t),t}$) to update $\pi^{t}$}
				% \For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
				\For{$a = 1, \dots, N$}{
					% \eIf{$\Alg_a$ was trusted, \ie, $A_a(t) = A(t)$}{
					\eIf{$\Alg_a$ was trusted, \ie, $A_a(t) = A(t)$}{
						$ \pi^{t+1}_{a} = \exp(\eta_t r(t)) \times \pi^{t}_{a} $
						\tcp*{Trusted more}
					}{
						% $ \pi^{t+1}_{a} = \exp(- \eta_t r(t) \times \pi^{t}_{a} $
						$ \pi^{t+1}_{a} = \pi^{t}_{a} $
						\tcp*{Do not update the trust now}
					}
				}
				Renormalize the new weights $\pi^{t+1}$: $\pi^{t+1} \eqdef \pi^{t+1} / \sum_{a=1}^{N} \pi^{t+1}_{a}$.
				% \tcp*{Project it back to $\Delta_N$}
			}
			\caption{Our algorithm \Aggr{} aggregating $\Alg_1,\dots,\Alg_N$.}
			\label{algo:25:Aggr}
		\end{algorithm}
		\end{framed}
	\end{figure}
\end{small}

@@

We compare our \Aggr{} algorithm,
as well as other aggregation algorithms, \ExpQ{} from \cite{Bubeck12},
\CORRAL{} from \cite{Agarwal16} and \LearnExp{} from \cite{Singla17}, all with their default parameters.
%
The aggregated algorithms consist in:
a naive uniform exploration (to have at least one algorithm with bad performances, \ie, linear regret, that is \emph{not} included in the plots to reduce clutter),
\UCB{} with $\alpha=1/2$, three \klUCB{} algorithms respectively using Bernoulli, Gaussian and exponential $\kl$ functions, and BayesUCB and Thompson sampling with uniform prior.

@@

We presented the use of aggregation algorithms in the context of Opportunistic Spectrum Access for Cognitive Radio,
especially for the real-world setting of unknown problem instances,
when tuning parameters before-hand is no longer possible and an adaptive algorithm is preferable.
% - \ExpQ and \Aggr works fine
% Both algorithms \ExpQ{} and \Aggr{} have been detailed, and we explained why
Our proposed \Aggr{} was presented in details,
and we also highlighted its differences with \ExpQ.
% as well \color{red} as the intuition that it seems more suited for purely stochastic problems\color{black}.

% - \Aggr{} really help to select the best algorithm against a certain problem, on the fly without any prior knowledge of the problem neither any prior knowledge on which algorithms is the best
We presented experiments on simple MAB problems coming from previous work on bandits for OSA \cite{Jouini10},
and the simulations results showed that \Aggr{} is able to identify on the fly the best algorithm to trust for a specific problem, as expected.
Experiments on problems mixing different families of distributions were also presented, with similar conclusions in favor of \Aggr.
% It is not presented in this section, but our proposed algorithm also works well in dynamic scenarios, in which the distribution of the arms can change abruptly at some time,
% and appears to be more robust than simple non-aggregated algorithms.

@@

\paragraph{Reproducility of the experiments.}
%
Experiments presented in this Section are based on our library SMPyBandits,
and the page \texttt{SMPyBandits.GitHub.io/Aggregation.html} gives instructions to reproduce them.

>>>>

\begin{small}
	\begin{figure}[h!]
		\centering
		\begin{framed}
		% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
		% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
		\begin{algorithm}[H]
			% XXX Input, data and output
			\KwIn{$N$ bandit algorithms, $\Alg_1, \dots, \Alg_N$, with $N \geq 2$}
			% \KwIn{Number of arms, $K \geq 2$}
			% \KwIn{Time horizon, $T \geq 1$, \textbf{not} used for the learning}
			\KwIn{A sequence of learning rates, $(\eta_t)_{t \geq 1}$}
			\KwData{Initial uniform distribution, $\pi^{0} = \cU([N])$}
			\KwResult{$\Alg_{\mathrm{aggr}}=\Aggr\left[\Alg_1, \dots, \Alg_N\right]$}
			% XXX Algorithm
			\For(\tcp*[f]{At every time step})
            {$t = 1, \dots, T$}{
				%
				% \tcp{First, run each algorithm $\Alg_a$}
				\For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
					$\Alg_a$ updates its internal state (e.g., \UCB{} indexes)\;
					It chooses $A_a(t) \in [K]$.
				}
				%
				% \tcp{The more algorithms have chosen arm $j$, the more probable it is to be chosen.}
				Let $p^{t}_j \eqdef \sum\limits_{a = 1}^{N} \pi^{t}_a \times \indic(\{A_a(t) = j\}), \;\forall 1\leq j \leq K$\;
				% \tcp*{Sum trusts}
				Then $\Alg_{\mathrm{aggr}}$ chooses arm $A(t) \sim p^{t}$\;
				% $\P(A(t)_{\mathrm{aggr}} = j) = p^{t}_j$
				% \tcp*{Sample once}
				%
				Give \emph{original} reward $(A(t), r(t))$ to \emph{each} $\Alg_a$ (maybe \emph{not} on its chosen arm)\;
				Compute an \emph{unbiased} estimate of the reward, $\widehat{r}(t) = r(t) / p^{t}_{A(t)}$\;
				% \tcp{Use bandit feedback to update $\pi^{t}$}
				% \tcp{Finally, use the instantaneous bandit feedback (reward $\ell_{A(t),t}$) to update $\pi^{t}$}
				% \For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
				\For{$a = 1, \dots, N$}{
					% \eIf{$\Alg_a$ was trusted, \ie, $A_a(t) = A(t)$}{
					\eIf{$\Alg_a$ was trusted, \ie, $A_a(t) = A(t)$}{
						$ \pi^{t+1}_{a} = \exp(\eta_t r(t)) \times \pi^{t}_{a} $
						\tcp*{Trusted more}
					}{
						% $ \pi^{t+1}_{a} = \exp(- \eta_t r(t) \times \pi^{t}_{a} $
						$ \pi^{t+1}_{a} = \pi^{t}_{a} $
						\tcp*{Do not update the trust now}
					}
				}
				Renormalize the new weights $\pi^{t+1}$: $\pi^{t+1} \eqdef \pi^{t+1} / \sum_{a=1}^{N} \pi^{t+1}_{a}$.
				% \tcp*{Project it back to $\Delta_N$}
			}
			\caption{Our algorithm \Aggr{} aggregating $\Alg_1,\dots,\Alg_N$.}
			\label{algo:25:Aggr}
		\end{algorithm}
		\end{framed}
	\end{figure}
\end{small}

@@

We compare our \Aggr{} algorithm,
as well as other aggregation algorithms, \ExpQ{} from \cite{Bubeck12},
\CORRAL{} from \cite{Agarwal16} and \LearnExp{} from \cite{Singla17}, all with their default parameters.
%
The aggregated algorithms consist in:
a naive uniform exploration (to have at least one algorithm with bad performances, \ie, linear regret, that is \emph{not} included in the plots to reduce clutter),
\UCB{} with $\alpha=1/2$, three \klUCB{} algorithms (resp. with Bernoulli, Gaussian and exponential $\kl$ functions), and BayesUCB and Thompson sampling with uniform prior.

@@

We presented the use of aggregation algorithms in the context of Opportunistic Spectrum Access for Cognitive Radio,
especially for the real-world setting of unknown problem instances,
when tuning parameters before-hand is no longer possible and an adaptive algorithm is preferable.
% - \ExpQ and \Aggr works fine
% Both algorithms \ExpQ{} and \Aggr{} have been detailed, and we explained why
Our proposed \Aggr{} was presented in details,
and we also highlighted its differences with \ExpQ.
% as well \color{red} as the intuition that it seems more suited for purely stochastic problems\color{black}.
%
% - \Aggr{} really help to select the best algorithm against a certain problem, on the fly without any prior knowledge of the problem neither any prior knowledge on which algorithms is the best
We presented experiments on simple MAB problems coming from previous work on bandits for OSA \cite{Jouini10},
and the simulations results showed that \Aggr{} is able to identify on the fly the best algorithm to trust for a specific problem, as expected.
Experiments on problems mixing different families of distributions were also presented, with similar conclusions in favor of \Aggr.
% It is not presented in this section, but our proposed algorithm also works well in dynamic scenarios, in which the distribution of the arms can change abruptly at some time,
% and appears to be more robust than simple non-aggregated algorithms.

@@

\paragraph{Reproducility of the experiments.}
%
Experiments presented in this Section are based on our library SMPyBandits,
and the page \href{https://SMPyBandits.GitHub.io/Aggregation.html}{\texttt{SMPyBandits.GitHub.io/Aggregation.html}} gives instructions to reproduce them.
